|

### 2019-11-18 analysis/paper/paper.Rmd
Add production efficiency to summary TS plot

```{r summary-ts-plot, fig.cap = summary_ts_cap}
### Figure 6
summary_ts_cap <- paste(
  htmlfig(),
  "ED2 plot-level predictions of",
  "net (NPP) primary productivity and",
  "total leaf area index (LAI),",
  "by model configuration.",
  "The dashed lines indicate the 10th and 90th quantiles of results.",
  "Black dot with error bars is the observed mean and min/max value."
  # TODO REF
)
fig("summary-ts-plot.png")
```

>>>>

```{r summary-ts-plot, fig.cap = summary_ts_cap}
### Figure 6
summary_ts_cap <- paste(
  htmlfig(),
  "ED2 plot-level predictions of",
  "net (NPP) primary productivity,",
  "total leaf area index (LAI),",
  "and production efficiency (NPP / LAI)",
  "by model configuration.",
  "Black dot with error bars is the observed mean and min/max value."
  # TODO REF
)
fig("summary-ts-plot.png")
```
